MixEth: efficient, trustless coin mixing service for Ethereum

### 2018-12-21 article/shortpaper/main.tex
Short paper ready

We implemented MixEth in Solidity with two different approaches. The first one does not apply state channels, all the transactions are made on-chain. This could lead to unwanted gas costs as the number of corrupted shuffles increases. One of our main motivation with MixEth is to provide an efficient and scalable coin mixing protocol which uses as little blockchain resources, storage and gas, as possible. Therefore we also implement and evaluate MixEth applying state channels, namely shuffling and challenging a shuffle occurs off-chain and only deposit and withdrawal transactions happen on-chain.
Both of the implementations allow users to mix Ether or other ERC20-compatible tokens.

@@

\begin{table}[H] 
	\caption{Proof-of-concept implementation gas cost results. MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
	\centering 
	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}} 	
		\toprule
		\hline
		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
		\cline{4-5}&&&Shuffle upload&Challenge\\
		\hline
		\midrule
		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
		MixEth&TBD&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
		MixEthChannel&TBD&TBD&0&0&TBD\\
		\bottomrule
	\end{tabular}
	\label{table:gasproperties}
\end{table} 
\newpage
\bibliographystyle{plain}
\bibliography{sample}

>>>>

We implemented MixEth in Solidity with two different approaches \footnote{https://github.com/seresistvanandras/MixEth}. The first one does not apply state channels, all the transactions are made on-chain. This could lead to unwanted gas costs as the number of corrupted shuffles increases. One of our main motivation with MixEth is to provide an efficient and scalable coin mixing protocol which uses as little blockchain resources, storage and gas, as possible. Therefore we also implement and evaluate MixEth applying state channels, namely shuffling and challenging a shuffle occurs off-chain and only deposit and withdrawal transactions happen on-chain.
Both of the implementations allow users to mix Ether or other ERC20-compatible tokens.

@@

\begin{table}[H] 
	\caption{Proof-of-concept implementation gas cost results. MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
	\centering 
	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}} 	
		\toprule
		\hline
		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
		\cline{4-5}&&&Shuffle upload&Challenge\\
		\hline
		\midrule
		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
		MixEth&5395945&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
		MixEthChannel&672276&21000&0&0&TBD\\
		\bottomrule
	\end{tabular}
	\label{table:gasproperties}
\end{table} 
\newpage
\bibliographystyle{plain}
\bibliography{sample}
